JuPOETs: A Constrained Multiobjective Optimization Approach to Estimate Biochemical Model Ensembles in the Julia Programming Language

### 2016-05-25 Paper_v1.tex
Name update / NSFGRF correction

\author[
   addressref={aff2},
   email={dmb457@cornell.edu}
]{\inits{DB}\fnm{David} \snm{Bassen}}
\author[
  addressref={aff1}
]{\inits{MV}\fnm{Michael} \snm{Vilkhovoy}}
\author[
  addressref={aff1}
]{\inits{MM}\fnm{Mason} \snm{Minot}}
\author[
   addressref={aff2},
   email={jtb47@cornell.edu}
]{\inits{JB}\fnm{Jonathan T} \snm{Butcher}}
\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={jdv27@cornell.edu}   % email address
]{\inits{JV}\fnm{Jeffrey D} \snm{Varner}}

@@

\section*{Funding}
This study was supported by an award from the National Science Foundation (NSF CBET-0955172) and the National Institutes of Health (NIH HL110328) to J.B, and by
a National Science Foundation Graduate Research Fellowship (NSGRF) to D.B.

>>>>

\author[
   addressref={aff2},
   email={dmb457@cornell.edu}
]{\inits{DB}\fnm{David M} \snm{Bassen}}
\author[
  addressref={aff1}
]{\inits{MV}\fnm{Michael} \snm{Vilkhovoy}}
\author[
  addressref={aff1}
]{\inits{MM}\fnm{Mason} \snm{Minot}}
\author[
   addressref={aff2},
   email={jtb47@cornell.edu}
]{\inits{JB}\fnm{Jonathan T} \snm{Butcher}}
\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={jdv27@cornell.edu}   % email address
]{\inits{JV}\fnm{Jeffrey D} \snm{Varner}}

@@

\section*{Funding}
This study was supported by an award from the National Science Foundation (NSF CBET-0955172) and the National Institutes of Health (NIH HL110328) to J.B, and by
a National Science Foundation Graduate Research Fellowship (NSFGRF) to D.B.
